% Section 2 in file desc.tex

% Section 2.1
\subsection{Project Motivation and Goals}

% Section 2.2
\subsection{Objectives}
\todo{3 pages}
In order to enable homeowners to have the best experience with their new WHCS
we will explain some core project objectives. These describe what the end-user
would be able to do with the system at a high level.

% Section 2.2.1
\subsubsection{Voice Control}
Voice control
from a supported Android device will allow the user to remotely activate any
part of the home that is integreated with WHCS. This would include activating
lights, unlocking doors, turning off and on applicances (by controlling their
respective outlets), quering sensors, and any other home specific applications.
All of these \emph{actions} and \emph{targets} will be able to be used just
from the user's voice. Voice actions will be specific to each target, but they
will consist of verbs such as \textbf{turn}, \textbf{query}, \textbf{check},
\textbf{open}, \textbf{close}, and so on. The list of targets will directly
correspond to the number of control modules listed in the home and their type.
This will be explained in more detail in Section \ref{sec:sys-design}.

% Section 2.2.2
\subsubsection{Light Activation}
Through activating lights and querying their status remotely, a homeowner will
no longer have to be present in the same room as the switch.  By connecting
lights to WHCS, they will become integrated in to the home network and not be
isolated in each room of the home.  With just a spoken command or a tap on
their smartphone, lights will be controlled.  By automating the process of
toggling light switches, WHCS will have the ability to be smart about when they
are ON or OFF, freeing the user from having to think about their state at all.
In addition, lights, just like all of the other connected control modules in
the home, will be able to be actuated on a specific schedule. This schedule
\todo{make a section for scheduling or remove} can be designed by the homeowner
to meet their daily lives or in a special circumstance, such as travel.

% Section 2.2.3
\subsubsection{Outlet Activation}
Lights aren't the only actionable think in the home. There are a multitude of
applicances throughout the home which could benefit from remote control. Some
of these include coffee makers, toasters, or computers\todo{find some better
examples}. If integrated with WHCS through outlet control, these appliances
would be able to be apart of the home network. Imagine being able to start the
morning coffee from the comfort of the bedroom. This would be possible with an
appropriate coffee maker and WHCS outlet control. An added benefit from having
outlets being automated is that there would be less draw from power leeching
devices' power subsystems, which may be always-on \todo{cite article showing
hyping up how much power you lose to leeches}.

% Section 2.2.4
\subsubsection{Door Access}

% Section 2.2.5
\subsubsection{Data Collection}
In order to give users a broad overview of their home's state, WHCS supports
the collection of data from \emph{arbitrary} sensors. Data collected can
include temperature, humidity, light level, sound levels, and so on. Each home
may have sensors throughout collecting various data that the homeowner deems
useful. The sensor integration with WHCS would be transparent to the user. All
they would see would be the list of sensors and the corresponding values.
WHCS's pluggable control module's would be tailored to each sensor or set of
sensors, which would relay their data back to the base station. The base
station would support queries from the LCD interface and simultaneously from a
connected phone.

Beyond home sensors, all of the the other controllable objects in the WHCS
would have metadata being collected about them at all times. This extra metadata
would include \textbf{connection status} and \textbf{power status}. See Section
\ref{sec:network-library} for a more detailed description of the supported
network packets and the type of fields they support.

All of this raw data being collected could be displayed to the user in the form of graphs and tables. It would serve as the basis for a set of statistics for display to the user.

% Section 2.3
\subsection{Requirements and Specifications}

% Section 2.4
\subsection{Research of Related Products}

% Section 2.4.1
\subsubsection{Z-Wave}

% Section 2.4.2
\subsubsection{Belkin}

% Section 2.4.3
\subsubsection{Apple HomeKit}

% Section 2.4.4
\subsubsection{Nest Labs}

