% Section 1 in file summary.tex
The Wireless Home Control System is meant to be a solution for any homeowner to
be able to remotely control core appliances of their home. The WHCS vision is
to allow the user to control lights, outlets, doors, and sensors around their
home. The system{}'s design philosophy emphasizes ease of use, affordability,
and effectiveness. An Android phone application developed for WHCS will allow
users to monitor the state of the installed components and activate them
remotely. A central base station equipped with a touch{}-enabled LCD will be
present to allow the users to interact with the system without the need of a
phone. Peripheral control modules will be installed into the targeted
appliances such as lights, outlets, and doors for WHCS to control. Together the
phone, base station, and peripheral control modules will constitute WHCS.

The implementation of such a system requires research in a myriad of fields to
produce a full{}-fledged product. Android software development is the core for
creating the users first impression with WHCS. Research must be conducted to
conform to the design philosophies of the Android ecosystem. The alternative
interface offered for WHCS will be the base station{}'s display, as a result
the best solution for a touch capable LCD will be examined. Communication
devices will form the foundation for the wireless aspect of WHCS, thus an
investigation into the advantages of different communication modules is
required to realize the system. A network protocol will need to be planned out
and implemented in order to form a unified system from the independent modules.
The activation of appliances around the home requires high voltage control, so
methodologies for properly harnessing the power provided by homes are a
requirement. To extend upon harnessing the home{}'s power, our individual
control modules and base station{}'s logic level voltage depend upon the
creation of an efficient way to step down the high voltage supplied to the
home. Efficient forms of rectification and power provision will need to be
researched for WHCS to be self{}-sufficient. Important research and critical
design decisions will go into the development of the printed circuit boards
that will provide the foundation for all the hardware of WHCS.

Wireless Home Control System is a solution targeting the masses and designed by
few. Naturally such a system will suffer from the constraints imposed upon the
creators. Most prominent of all constraints are those stemming from economics.
The development and production of WHCS will have to conform to the low budget
available. Design decisions will be made to minimize overall cost of the system
to satisfy this constraint. WHCS has the potential for mass implementation if
user reception is positive so the design will adhere to manufacturing
constraints. The parts used in the system will be chosen so that they are
widely available. Our boards and parts will be designed so that they are easy
to replicate and manufacture. With a product such as WHCS health and safety is
clearly an issue. The system is meant to be installed inside the home where the
user should feel at ease with the system installed. Thus it is ethical for us to
put effort into making the system safe to use. Things such as controlling the
home{}'s high voltage will have to be done in a safe manner. Security is
another strong constraint attributed to products targeting the home. The system
will be designed to maximize security for our users.
